\vspace{-0.25em}\thetitle

### 2009-07-17 paper.tex
...

The fundamental concept underlying these works is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to points in a vector space;
each dimension of the representation describes some aspect of flow behavior.
The representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix:
each flow is mapped to a row of the matrix.

@@

The key observation of this work is that real-world network traces tend to have approximately low-rank representation matrices.

>>>>

The fundamental concept underlying these works is \emph{linear representation of network traffic}~\cite{Karpinski08}.
A linear representation is a function that maps sets of flows to points in a vector space;
each dimension of the representation describes some aspect of flow behavior.
The representation must also satisfy a simple linearity condition which we will describe in detail later.
% the sum of the representations of a set of flows is a vector that represents the aggregate behavior of the set of flows.
An entire traffic trace may be represented as a matrix where each row is the linear representation of a flow in the trace.
We restrict our consideration to a particularly natural and powerful class of representations whose coordinates describe the frequencies of flow features.
For example, let there be a dimension for each packet size up to 1500.
Each coordinate indicates the number of packets in a set of flows of that size.
\caps{IP} protocol type, port numbers, and inter-packet intervals can be handled similarly.
% Examples of flow features are the number of packets of a certain size or the use of a particular port number.
% The fundamental premise of this work, and of the sequel, is that the representatives of actual flow behaviors can be understood as being sampled from

Our key observation is that real-world network traces tend to have approximately low-rank representation matrices despite the potential rank of such matrices being very large.
Moreover, most flows' vectors lie on only one of a few even lower rank subspaces.
Real traffic lies near the union of a small set of very low rank subspaces in the huge potential space of representations.
Moreover, the low-rank subspace near which real traffic lies can be decomposed into subspaces of even lower rank, with almost all flows lying in one of these subspaces.
Typically, these smaller subspaces are one-dimensional, but in some cases they may have up to a dozen dimensions.

% the vast majority of observed flow behaviors in any given trace lie in one of a handful low-rank subspaces.
% These subspaces are mostly of rank one, but a few have dimensions as high as ten.

@@
